Reduced plasticity and opportunity for selection in terrestrial ectotherm populations

### 2023-04-13 ms.qmd
Still not converging. Going to try spline of lat and long instead

   model5_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type*habitat + long.x*lat.y + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.99, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)

>>>>

   model5_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type*habitat + s(long.x) + s(lat.y) + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.99, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)
